---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Experiment Calculator

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
<!-- badges: end -->

The goal of Experiment Calculator is to provide a simple calculator to plan, analyse and diagnose simple experiments.

## Installation

You can install the development version of ExperimentCalculator like so:

```{r install, warning=FALSE, error=FALSE, results='hide'}
devtools::install_github('sabush/ExperimentCalculator')

```

## Load the Calculator

To load the power and significance calculator, load the library and run the app

```{r example}
library(ExperimentCalculator)
#ExperimentCalculator::run_app() # Uncomment to run the app
```

Further usage of the app can be found in the vignettes.

## Code of Conduct
  
Please note that the ExperimentCalculator project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
